Building a GNU/Hurd Cluster

### 2018-01-21 slides/cua.tex
slides - change calling convention for \task and \queue macros

\begin{tikzpicture}[transform canvas={scale=0.4, yshift=12em, xshift=-15em}]

\task{Task 1 left}{0,0}{ru}{}
\task{Task 2 left}{0,-11 em}{ru}{}
\task{Task 3 left}{0,-22 em}{ru}{}
\task{Task 4 left}{0,-33 em}{ru}{}
\task{Task 1 right}{30 em,0}{lu}{}
\task{Task 2 right}{30 em,-11 em}{lu}{}
\task{Task 3 right}{30 em,-22 em}{lu}{}
\task{Task 4 right}{30 em,-33 em}{lu}{}

\queue{Task 1 right Port 5}{queue 1}
\queue{Task 2 right Port -5}{queue 2a}
\queue{Task 2 right Port 5}{queue 2b}
\queue{Task 3 right Port 0}{queue 3}
\queue{Task 4 right Port 0}{queue 4}

@@

\task{Task 1}{0,0}{r}{
\node (message1) [message] {Message 1};
}
\task{Task 2}{15 em,0}{l}{
\node (message2) [message] at (1 em, 1 em) {Message 1};
\node (message2a) [message] at (1.9 em, -1 em) {Message 2};
}
\task{Task 3}{0,-11 em}{r}{
\node (message3) [message] {Message 2};
}

@@

\task{Task 1}{0,0}{br}{
% print two sendright nodes, one to fill the message1 box to the correct size,
% and another one to actually draw it, since message1 will overwrite the
% first sendright
\only<2->{
\node (sendright) [draw, fill=orange] {Send 41};
\node (message1) [fit=(sendright), message] {Message 1};
\node (sendright) [draw, fill=orange] {Send 41};
}

@@

\task{Task 2}{15 em,0}{bl}{
\only<3->{
\node (sendright2) [draw, fill=orange] {Send 9};
\node (message2) [fit=(sendright2), message] {Message 1};
\node (sendright2) [draw, fill=orange] {Send 9};
}

@@

\task{Task 1}{0,0}{br}{
% print two sendright nodes, one to fill the message1 box to the correct size,
% and another one to actually draw it, since message1 will overwrite the
% first sendright
\only<2->{
\node (sendright) [draw, fill=green] {Recv 41};
\node (message1) [fit=(sendright), message] {Message 1};
\node (sendright) [draw, fill=green] {Recv 41};
}

@@

\task{Task 2}{15 em,0}{bl}{
\only<3->{
\node (sendright2) [draw, fill=green] {Recv 9};
\node (message2) [fit=(sendright2), message] {Message 1};
\node (sendright2) [draw, fill=green] {Recv 9};
}

@@

\task{Task 1}{0,0}{br}{
% print two sendright nodes, one to fill the message1 box to the correct size,
% and another one to actually draw it, since message1 will overwrite the
% first sendright
\node (message1) [message] {Message};
\only<1>{
\node (memory1) [below=1em, fill=orange!40, minimum size=2cm, dashed, thick, draw] at (message1.south) {Memory};
\draw [thick, color=red, dotted, -] (message1) -- (memory1);
}
}

\task{Task 2}{15 em,0}{bl}{
\only<2->{
\node (message2) [message] {Message};
\node (memory2) [below=1em, fill=orange!40, minimum size=2cm, dashed, thick, draw] at (message2.south) {Memory};
\draw [thick, color=red, dotted, -] (message2) -- (memory2);
}
}

@@

\task{ext2 File Server}{20 em,-5 em}{l}{}
\task{httpfs}{20 em, -12 em}{ls}{}
\task{pfinet}{20 em, -17 em}{ls}{}

@@

\task{Filesystem Server}{0,0}{}{
\node (memory1) [above left=-0.5, fill=white, minimum size=1.5cm, dashed, thick, draw] {};
}
\task{ls}{15 em,0}{}{
%\node (memory1) [above right=-0.5, fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
\node (memory2) [above right=-0.5, fill=white, minimum size=1.5cm, dashed, thick, draw] {};
\node [below] at (memory2.north) {\tiny addr};
}

@@

\task{Task 1}{-5em,0}{}{
\node (memory1) [fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
}
\task{Task 2}{6 em,0}{}{
\node (memory2) [fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
}
\task{Task 3}{17 em,0}{}{
\node (memory3) [fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
}

@@

\task{Task 1}{-5em,0}{u}{
\only<1-2,9->{\node (memory1) [emptymemory] {\only<2>{\Huge R}};}
\only<3-8> {\node (memory1) [readmemory, dashed] {};}
}
\task{Task 2}{6 em,0}{u}{
\only<1-3,9->{\node (memory2) [emptymemory] {};}
\only<4-8>{\node (memory2) [readmemory, dashed] {};}
}
\task{Task 3}{17 em,0}{u}{
\only<1-3,9-13>{\node (memory3) [emptymemory] {\only<11->{\Huge W}};}
\only<4-8>{\node (memory3) [readmemory, dashed] {};}
\only<14->{\node (memory3) [writememory, dashed] {};}
}

@@

\task{Task 4}{-5em,-40 em}{u}{
\node (memory4) [emptymemory] {};
}
\task{Task 5}{6 em,-40 em}{u}{
\only<1-5,13->{\node (memory5) [emptymemory] {\only<5>{\Huge R}};}
\only<6-12>{\node (memory5) [readmemory, dashed] {};}
}
\task{Task 6}{17 em,-40 em}{u}{
\only<1-9,13->{\node (memory6) [emptymemory] {\only<7-9>{\Huge W}};}
\only<10-12>{\node (memory6) [writememory, dashed] {};}
}

@@

\task{Task 1}{-5em,0}{u}{}
\task{Task 2}{6 em,0}{u}{}
\task{Task 3}{17 em,0}{u}{}

@@

\task{Task 4}{-5em,-40 em}{u}{}
\task{Task 5}{6 em,-40 em}{u}{}
\task{Task 6}{17 em,-40 em}{u}{}

@@

\task{Task 1}{-30 em,0}{r}{
  \only<1-2>{
    \node (sendright) [draw, fill=orange, inner xsep=5] {Send};
    \node (message1) [fit=(sendright), message] {Message};
    \only<1>{\node (sendright) [draw, fill=orange, inner xsep=5] {Send};}
  }
}
\task{netmsg 1}{-15 em,0}{l}{
  \only<2-3>{
    \node (sendright2) [draw, fill=orange, inner xsep=5] {Send};
    \node (message2) [fit=(sendright2), message] {Message};
  }
  \only<2->{\node (sendright2) [draw, fill=orange, inner xsep=5] {Send};}
}

@@

\task{netmsg 2}{15 em,0}{r}{
  \only<3-5>{
    \node (sendright3) [draw, fill=orange, inner xsep=5] {Send};
    \node (message3) [fit=(sendright3), message] {Message};
    \only<4>{\node (sendright3) [draw, fill=orange, inner xsep=5] {Send};}
  }
  \only<4->{\node (rcvright3) [draw, fill=green, inner xsep=5] at (0,1.25) {Rcv};}
}
\task{Task 2}{30 em,0}{l}{
  \only<5>{
    \node (sendright4) [draw, fill=orange, inner xsep=5] {Send};
    \node (message4) [fit=(sendright4), message] {Message};
  }
  \only<5-6>{\node (sendright4) [draw, fill=orange, inner xsep=5] {Send};}
}

>>>>

% node distance is the distance that the queues are positioned from their task ports
\begin{tikzpicture}[transform canvas={scale=0.4, yshift=12em, xshift=-15em}, node distance=6em]

\task{Task 1 left}{at (0,0)}{ru}{}
\task{Task 2 left}{at (0,-11em)}{ru}{}
\task{Task 3 left}{at (0,-22em)}{ru}{}
\task{Task 4 left}{at (0,-33 em)}{ru}{}
\task{Task 1 right}{at (30 em,0)}{lu}{}
\task{Task 2 right}{at (30 em,-11 em)}{lu}{}
\task{Task 3 right}{at (30 em,-22 em)}{lu}{}
\task{Task 4 right}{at (30 em,-33 em)}{lu}{}

\queue[left = of Task 1 right Port 5]{queue 1}{}
\queue[left = of Task 2 right Port -5]{queue 2a}{}
\queue[left = of Task 2 right Port 5]{queue 2b}{}
\queue[left = of Task 3 right Port 0]{queue 3}{}
\queue[left = of Task 4 right Port 0]{queue 4}{}

@@

\task{Task 1}{at (0,0)}{r}{
\node (message1) [message] {Message 1};
}
\task{Task 2}{at (15 em,0)}{l}{
\node (message2) [message] at (1 em, 1 em) {Message 1};
\node (message2a) [message] at (1.9 em, -1 em) {Message 2};
}
\task{Task 3}{at (0,-11 em)}{r}{
\node (message3) [message] {Message 2};
}

@@

\task{Task 1}{at (0,0)}{br}{
% print two sendright nodes, one to fill the message1 box to the correct size,
% and another one to actually draw it, since message1 will overwrite the
% first sendright
\only<2->{
\node (sendright) [draw, fill=orange] {Send 41};
\node (message1) [fit=(sendright), message] {Message 1};
\node (sendright) [draw, fill=orange] {Send 41};
}

@@

\task{Task 2}{at (15 em,0)}{bl}{
\only<3->{
\node (sendright2) [draw, fill=orange] {Send 9};
\node (message2) [fit=(sendright2), message] {Message 1};
\node (sendright2) [draw, fill=orange] {Send 9};
}

@@

\task{Task 1}{at (0,0)}{br}{
% print two sendright nodes, one to fill the message1 box to the correct size,
% and another one to actually draw it, since message1 will overwrite the
% first sendright
\only<2->{
\node (sendright) [draw, fill=green] {Recv 41};
\node (message1) [fit=(sendright), message] {Message 1};
\node (sendright) [draw, fill=green] {Recv 41};
}

@@

\task{Task 2}{at (15 em,0)}{bl}{
\only<3->{
\node (sendright2) [draw, fill=green] {Recv 9};
\node (message2) [fit=(sendright2), message] {Message 1};
\node (sendright2) [draw, fill=green] {Recv 9};
}

@@

\task{Task 1}{at (0,0)}{br}{
% print two sendright nodes, one to fill the message1 box to the correct size,
% and another one to actually draw it, since message1 will overwrite the
% first sendright
\node (message1) [message] {Message};
\only<1>{
\node (memory1) [below=1em, fill=orange!40, minimum size=2cm, dashed, thick, draw] at (message1.south) {Memory};
\draw [thick, color=red, dotted, -] (message1) -- (memory1);
}
}

\task{Task 2}{at (15 em,0)}{bl}{
\only<2->{
\node (message2) [message] {Message};
\node (memory2) [below=1em, fill=orange!40, minimum size=2cm, dashed, thick, draw] at (message2.south) {Memory};
\draw [thick, color=red, dotted, -] (message2) -- (memory2);
}
}

@@

\task{ext2 File Server}{at (20 em,-5 em)}{l}{}
\task{httpfs}{at (20 em, -12 em)}{ls}{}
\task{pfinet}{at (20 em, -17 em)}{ls}{}

@@

\task{Filesystem Server}{at (0,0)}{}{
\node (memory1) [above left=-0.5, fill=white, minimum size=1.5cm, dashed, thick, draw] {};
}
\task{ls}{at (15 em,0)}{}{
%\node (memory1) [above right=-0.5, fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
\node (memory2) [above right=-0.5, fill=white, minimum size=1.5cm, dashed, thick, draw] {};
\node [below] at (memory2.north) {\tiny addr};
}

@@

\task{Task 1}{at (-5em,0)}{}{
\node (memory1) [fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
}
\task{Task 2}{at (6 em,0)}{}{
\node (memory2) [fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
}
\task{Task 3}{at (17 em,0)}{}{
\node (memory3) [fill=orange!40, minimum size=1.5cm, dashed, thick, draw] {};
}

@@

\task{Task 1}{at (-5em,0)}{u}{
\only<1-2,9->{\node (memory1) [emptymemory] {\only<2>{\Huge R}};}
\only<3-8> {\node (memory1) [readmemory, dashed] {};}
}
\task{Task 2}{at (6 em,0)}{u}{
\only<1-3,9->{\node (memory2) [emptymemory] {};}
\only<4-8>{\node (memory2) [readmemory, dashed] {};}
}
\task{Task 3}{at (17 em,0)}{u}{
\only<1-3,9-13>{\node (memory3) [emptymemory] {\only<11->{\Huge W}};}
\only<4-8>{\node (memory3) [readmemory, dashed] {};}
\only<14->{\node (memory3) [writememory, dashed] {};}
}

@@

\task{Task 4}{at (-5em,-40 em)}{u}{
\node (memory4) [emptymemory] {};
}
\task{Task 5}{at (6 em,-40 em)}{u}{
\only<1-5,13->{\node (memory5) [emptymemory] {\only<5>{\Huge R}};}
\only<6-12>{\node (memory5) [readmemory, dashed] {};}
}
\task{Task 6}{at (17 em,-40 em)}{u}{
\only<1-9,13->{\node (memory6) [emptymemory] {\only<7-9>{\Huge W}};}
\only<10-12>{\node (memory6) [writememory, dashed] {};}
}

@@

\task{Task 1}{at (-5em,0)}{u}{}
\task{Task 2}{at (6 em,0)}{u}{}
\task{Task 3}{at (17 em,0)}{u}{}

@@

\task{Task 4}{at (-5em,-40 em)}{u}{}
\task{Task 5}{at (6 em,-40 em)}{u}{}
\task{Task 6}{at (17 em,-40 em)}{u}{}

@@

\task{Task 1}{at (-30 em,0)}{r}{
  \only<1-2>{
    \node (sendright) [draw, fill=orange, inner xsep=5] {Send};
    \node (message1) [fit=(sendright), message] {Message};
    \only<1>{\node (sendright) [draw, fill=orange, inner xsep=5] {Send};}
  }
}
\task{netmsg 1}{at (-15 em,0)}{l}{
  \only<2-3>{
    \node (sendright2) [draw, fill=orange, inner xsep=5] {Send};
    \node (message2) [fit=(sendright2), message] {Message};
  }
  \only<2->{\node (sendright2) [draw, fill=orange, inner xsep=5] {Send};}
}

@@

\task{netmsg 2}{at (15 em,0)}{r}{
  \only<3-5>{
    \node (sendright3) [draw, fill=orange, inner xsep=5] {Send};
    \node (message3) [fit=(sendright3), message] {Message};
    \only<4>{\node (sendright3) [draw, fill=orange, inner xsep=5] {Send};}
  }
  \only<4->{\node (rcvright3) [draw, fill=green, inner xsep=5] at (0,1.25) {Rcv};}
}
\task{Task 2}{at (30 em,0)}{l}{
  \only<5>{
    \node (sendright4) [draw, fill=orange, inner xsep=5] {Send};
    \node (message4) [fit=(sendright4), message] {Message};
  }
  \only<5-6>{\node (sendright4) [draw, fill=orange, inner xsep=5] {Send};}
}
